Individual and Differential Harm in Redistricting

### 2025-08-25 paper/harm.qmd
more appx

>>>>

Even when the choice of constraints maps onto legal requirements, it is important to ensure that the counterfactual plans are similar to the enacted plan on discretionary criteria as well.
For example, a mapdrawer may weakly respect something like compactness or respecting county boundaries without being required to do so.
In this case, if these optional constraints are not matched in the counterfactual, it will be unclear whether any estimated harm is due to *actual* biases in a plan or the mismatch in criteria.
As such, it is important to not just ensure that any counterfactual samples use methods with known sampling properties, but also that the sampled plans are similar to the enacted plan on these discretionary criteria.
